Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2023-11-26 demystify.tex
update

\subsection{References}
\begin{itemize}
\item \href{http://www.pl-enthusiast.net/2022/10/03/how-to-write-a-grad-school-personal-statement/}{How to Write a Grad School Personal Statement} by Mike Hicks, 10/03/22
\end{itemize}
% \subsection{Outline of a LOR}\label{sec:lor-outline}

@@

Ultimately, choose a prof. that fits you the most by communicating with them, taking their courses, meeting them, asking them questions, and even talking to their current students. Indeed all this takes a lot of time and effort, but remember, you will be working with this person for 4-5 years, so it is important to try to find the right one.

@@

\subsection{Tenured, Tenure Track, Teaching,  Assistant Profs., Associate Profs, and Other Academic Titles}\label{sec:faculty-types}

@@

\subsubsection{References}
\begin{itemize}
    \item \href{https://yonatanbisk.com/emailing_professors.html}{Emailing Professors} by Yonatan Bisk
\end{itemize}

>>>>

\subsection{References}
\begin{itemize}
\item \href{http://www.pl-enthusiast.net/2022/10/03/how-to-write-a-grad-school-personal-statement/}{How to Write a Grad School Personal Statement} by Mike Hicks
\end{itemize}
% \subsection{Outline of a LOR}\label{sec:lor-outline}

@@

Ultimately, choose a prof. that fits you the most by communicating with them, taking their courses, meeting them, asking them questions, and even talking to their current students. Doing these takes a lot of time and effort, but remember, you will be working with this person for 5+ years, so it is important to try to find the right one.

@@

\subsubsection{References}
\begin{itemize}
    \item \href{https://www.cs.columbia.edu/wp-content/uploads/2019/03/Get-Advisor.pdf}{The Definitive "what do I ask/look for" in a PhD Advisor Guide}
\end{itemize}
\subsection{Tenured, Tenure Track, Teaching,  Assistant Profs., Associate Profs, and Other Academic Titles}\label{sec:faculty-types}

@@

\subsubsection{References}
\begin{itemize}
    \item \href{https://yonatanbisk.com/emailing_professors.html}{A Note about Emailing Professors} by Yonatan Bisk
\end{itemize}
